\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{hyperref}

\title{COMP SCI 4TB3\\ Development Plan\\ Python Enhancements:\\External-Local Argument Names, Do-While Loops, Switch-Case Statements \& Pattern Matching}

\author{ Authored By:
		\\ Ahmed, Zak
		\\ Oliveira, Pedro
		\\ Selvathayabaran, Piranaven
}

\date{}


\begin{document}



\newpage

\maketitle

The following official document is an agreed upon plan on how the COMP SCI 4TB3 ``Final Project" will be carried out. It contains information regarding how the project will be managed, implemented, reveiwed and any other critical details that need to be defined. The Developement Plan is subject to change and any modifications will be noted in the Revision History Section. 

\tableofcontents 

\newpage 

\section {Project Description}
The project for the course COMP SCI 4TB3 - Syntax Based Tools and Compilers will be to apply the knowledge gained from the course. Group 5, comprised of Pedro, Piranaven \& Zak will work together to enhance Python in four ways. Firstly, adding a Swift-like \textbf{External-Internal Function Argument Names} to Python. This would allow a function be called in an expressive, sentence-like manner, while still providing a function body that is readable and clear in intent.  After this,  we will add two language constructs: \textbf{Do-While Loops} \& \textbf{Switch-Case Statements}. Lastly, we will add Python function definitions with \textbf{Pattern Matching} as seen in functional programming. These would provide developers with more flexibility. Overall, this project will enhance our knowledge of Python Virtual Machines, the CPython grammar and much more.
 
 \section{Project Schedule}

\begin{tabular}{ |p{2cm}|p{9cm}| }
 \hline
 \multicolumn{2}{|c|}{Weekly Project Schedule} \\
 \hline
 Date & Milestone \\
  \hline
Week 1 & Adding Internal and External Function Argument Names\\
Week 2 & Language construct: Do-While Loop and Switch-Case \\
Week 3 & Language construct: Pattern Matching\\
Week 4 & Poster and presentation \\
 \hline
\end{tabular}
\linebreak
\par{\textbf{Division of Work:} Each team member will be expected to contribute to each milestone leading up to the final presentation.}
 
\section{Team Meeting Plan}
The team plans to meet every Monday, Tuesday \& Friday at the pre-defined times listed below. These dates and times are subject to change. A member of the team will email Dr.Sekerinski to organize a meeting in case it is needed.\newline 

\begin{tabular}{ |p{2cm}||p{3cm}|p{5cm}|  }
 \hline
 \multicolumn{3}{|c|}{Weekly Meeting Schedule} \\
 \hline
 Date &Time  & Location\\
 \hline
Monday &   12:30PM - 2:30PM   & Thode Library Room TBD\\
Tuesday &   12:30PM - 2:30PM   & Thode Library Room TBD\\
Friday  & 1:30PM - 3:30PM & Thode Library Room TBD\\

 \hline
\end{tabular}
\section{Team Communication Plan}

The team has decided on three lines of communication:

\begin{enumerate}
\item \textbf{GitLab}: Utilized for communcation on tasks related to the project implementation. Information relevant to all stakeholders and may be needed for future use should be posted here.  Comments should be made on Gitlab issues such that all parties are aware of details and rationales for decisions.
\item \textbf{Email}: This is for any communcations with Dr.Sekerinski, the TA's and any other third party. These are meant to be formal in nature.
\item \textbf{Facebook(Messenger)}: Used for the initial communication between group members. Change in meeting plans and confirmation of meeting times will be conducted through here if more convenient.
\end{enumerate}

\section{Team Member Roles}

\textbf{Scrum Master -\emph{Piranaven}}: In charge of making sure GitLab is up to date and in standard . Tasks are well formed and divided equally amongst agile team members. Responsible for  speaking to internal and external stakeholders to ensure issues are created and work is documented. \newline
\textbf{Note Taker- \emph{Zak}}:  Responsible for taking detailed notes during meeting's with Dr.Sekerinski or the TA's. Also, in charge of taking meeting minutes during team meetings  scrums, standups, retrospectives, etc. \newline
\textbf{Repo Administrator - \emph{Pedro}}:  Responsible for ensuring that the GitLab Repo is up to date. In charge of making sure README.md's are accurate and verifying any commits, merges, issues created are of standard.   \newline
\textbf{Developer - \emph{Piranaven, Zak, Pedro}}: Responsible for abiding by the coding style rules listed below. Responsible for delivering high quality code which meet the requirements of the tasks created. Provide insight towards design and development decisions.  \newline




\section{Technology}

\textbf{Programming Language :} Python, C\newline
\textbf{IDE:}  Visual Studio Code, Atom, Sublime, etc. There are no restrictions\newline 
\textbf{Testing Framework :} PyTest  - https://docs.pytest.org/en/latest/\newline
\textbf{Documentation Generation :} Sphinx - http://www.sphinx-doc.org/en/master/\newline 



\section{Resources}
\href{https://www.python.org}{Python Language}\newline
\href{https://docs.python.org/3/reference/grammar.html}{Python Grammar}\newline
\href{https://www.python.org/dev/peps/pep-3103/}{PEP 3103 -- A Switch/Case Statement}



\newpage
\section{Revision History}
\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
March 13th, 2019 &Piranaven Selva & Make Foundation for Development Plan\\
March 14th, 2019 &Zak Ahmed & Made Project Schedule\\
March 15th, 2019 &Pedro Oliveira & Added Project Description\\
\\
\bottomrule
\end{tabularx}
\end{table}

\end{document}